### 2019-08-22 reports/thesis/chapters/5_inference.tex
Adjust DefectExample
DefectExample is now an experiment
Supress warning when saving java object
Change parameter ordering in PlaneMultLine
Added p value plot in inference
EmpiricalNullFilter saves the image correctly transposed

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectDustExample_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ Gaussian image with \emph{speckle} defect is shown in a). The image was contaminated in b) and then filtered with kernel radius 20 in c). Defected pixels have the distribution $\normal(3,1)$. The speckle defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. In a), c) and d), highlighted in red are pixels tested as positive at the 5\% FDR level.}
  \label{fig:inference_defectDustExample}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectLineExample_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ Gaussian image with a \emph{line} defect is shown in a). The image was contaminated in b) and then filtered with kernel radius 20 in c). Defected pixels have the distribution $\normal(3,1)$. The line defect is 5 pixels thick. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. In a), c) and d), highlighted in red are pixels tested as positive at the 5\% FDR level.}
  \label{fig:inference_defectLineExample}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquareExample_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a). The image was contaminated in b) and then filtered with kernel radius \emph{20} in c). Defected pixels have the distribution $\normal(3,1)$. The square defect is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. In a) and c), highlighted in red are pixels tested as positive at the 5\% FDR level.}
  \label{fig:inference_defectSquareExample}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imagePreContaminated.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_imageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/defectSquare2Example_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a). The image was contaminated in b) and then filtered with kernel radius \emph{40} in c). Defected pixels have the distribution $\normal(3,1)$. The square defect is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. In a) and c), 
  highlighted in red are pixels tested as positive at the 5\% FDR level.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

@@

>>>>

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_imageClean.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_EmpiricalNullFilterimageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_EmpiricalNullFilternullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ Gaussian image with \emph{speckle} defect is shown in a). The image was contaminated in b) and then filtered with kernel radius 20 in c). Defected pixels have the distribution $\normal(3,1)$. The speckle defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. In a), c) and d), highlighted in red are pixels tested as positive at the 5\% FDR level.}
  \label{fig:inference_defectDustExample}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_imageClean.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_EmpiricalNullFilterimageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_EmpiricalNullFilternullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ Gaussian image with a \emph{line} defect is shown in a). The image was contaminated in b) and then filtered with kernel radius 20 in c). Defected pixels have the distribution $\normal(3,1)$. The line defect is 5 pixels thick. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. In a), c) and d), highlighted in red are pixels tested as positive at the 5\% FDR level.}
  \label{fig:inference_defectLineExample}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_imageClean.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_EmpiricalNullFilterimageFiltered.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_EmpiricalNullFilternullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a). The image was contaminated in b) and then filtered with kernel radius \emph{20} in c). Defected pixels have the distribution $\normal(3,1)$. The square defect is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. In a) and c), highlighted in red are pixels tested as positive at the 5\% FDR level.}
  \label{fig:inference_defectSquareExample}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_imageClean.eps}
        \caption{Uncontaminated}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_imageContaminated.eps}
        \caption{Contaminated}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilternullStd.eps}
        \caption{Filtered}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilternullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ Gaussian image with a \emph{square} defect is shown in a). The image was contaminated in b) and then filtered with kernel radius \emph{40} in c). Defected pixels have the distribution $\normal(3,1)$. The speckle defect has density $\pi_1 = 0.1$. The line defect is 5 pixels thick. The square defect is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. In a) and c), highlighted in red are pixels tested as positive at the 5\% FDR level.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleDust_EmpiricalNullFilterpValueFiltered.eps}
        \caption{Dust defect, $r=20$}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleLine_EmpiricalNullFilterpValueFiltered.eps}
        \caption{Line defect, $r=20$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare20_EmpiricalNullFilterpValueFiltered}
        \caption{Square defect, $r=20$}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectExampleSquare40_EmpiricalNullFilterpValueFiltered}
        \caption{Square defect, $r=40$}
      \end{subfigure}
    }
  \caption{A $256 \times 256$ contamined defected Gaussian image was filtered using the empirical null filter with kernel radius $r$. Shown are the values of the image converted to $p$-values. Defected pixels have the distribution $\normal(3,1)$. The square defect is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The critical region is for testing at the 5\% FDR level.}
  \label{fig:inference_defectExamplePValue}
\end{figure}

@@

Figure \ref{fig:inference_defectExamplePValue} shows the $p$-values after filtering a contaminated defected image. The FDR can be estimated in these figures by dividing the number of null statistics in the critical region by the number of statistics in the critical region. With a sensible kernel radius, some of the defects can be detected. False negatives do appear but this is inevitable in order to control for the FDR. The figure shows that using a kernel radius of $r=20$ for the square defect detected no pixels for defects. This, again, emphasise the importance of a good kernel radius.
